Multi-view 3D Aerosol Distribution Recovery

### 2013-07-28 article.tex
work on citations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Optical lightfield and integral
imaging~\cite{bishop,horstmeyer,kim,Ng1948} samples the optical
radiance distribution in location and direction. It is mainly used in
small-scale setups. This paper deals with a far larger scale, to
estimate scatterer 3D spatial distribution in the sky.  The atmosphere
allows light to pass through in multiple locations and
directions. Light is affected by this medium. Therefore, in this paper
we lay out a principle to recover this 3D distribution using measured
and modeled light-fields (Fig.~\ref{fig:groundgrid}).
\begin{figure*}[t!]
  \begin{center}
    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}
3D recovery of this medium has direct implications to various
scientific communities that either rely on remotely-sensed imagery,
study the atmosphere, or overcome the medium to see beyond. These
include meteorology, atmospheric sciences, volcanology, and
climatology.  Aerosol retrieval is important for understanding climate
evolution~\cite{Dayan2008,kalashnikova} and monitoring air
quality. Mapping aerosol density is significant to aviation safety,
which needs real time assessment of conditions and visibility around
flight paths.

In remote sensing~\cite{diner}, imaging through air is associated with
{\em atmospheric correction}, based on {\em aerosol retrieval}. In
this discipline, the atmosphere is often assumed to be plane-parallel,
using one-dimensional vertical RT. Consequently state-of-the-art
aerosol retrieval is done in distinct large lateral
blocks~\cite{Martonchikc} with limited height
resolution~\cite{kalashnikova}. We, however, seek 3D
recovery. Atmospheric correction is related to
dehazing~\cite{Joshi2010,Zhu2013}. In this paper, however, the medium
itself, at all relevant altitudes is the object of interest.

We rely on sky imaging from multiple directions and locations. Such
projection is similar to tomography in other scientific
domains~\cite{Arridge}. However, the situation here is distinct. Most
tomography setups have a controlled and/or multidirectional radiation
source~\cite{Boas2001,messer}. In contrast, our source is the
uncontrolled, unidirectional Sun. Moreover, typical tomography relies
on a linear model~\cite{gregson}: the pixel value is a linear
combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect
gases~\cite{Kazahaya2008,Price2001,Cosofret2009,wright}, which absorb
UV or IR radiation. However, aerosol attenuation of visible light is
typically dominated by {\em scattering}, rather than absorption. Since
the radiation source is single and fixed in space and time, we cannot
rely on direct illumination for tomographic recovery of attenuation
fields~\cite{Aviles2011}. We may only use sunlight scattered into the
LOS. The model is {\em nonlinear, yet tractable}. We model passive
optical tomographic imaging of 3D atmospheric scatterer distributions
in cloudless conditions. Then, we solve this tomography problem, to
recover the distribution. Recovery is formulated as an optimization
that minimizes a cost function. We derive the gradient of this cost
function, to enable efficient optimization.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Optical lightfield and integral
imaging~\cite{Stern2006,kim,Ng1948} samples the optical
radiance distribution in location and direction. It is mainly used in
small-scale setups. This paper deals with a far larger scale, to
estimate scatterer 3D spatial distribution in the sky.  The atmosphere
allows light to pass through in multiple locations and
directions. Light is affected by this medium. Therefore, in this paper
we lay out a principle to recover this 3D distribution using measured
and modeled light-fields (Fig.~\ref{fig:groundgrid}).
\begin{figure*}[t!]
  \begin{center}
    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}
3D recovery of this medium has direct implications to various
scientific communities that either rely on remotely-sensed imagery,
study the atmosphere, or overcome the medium to see beyond. These
include meteorology, atmospheric sciences, volcanology, and
climatology.  Aerosol retrieval is important for understanding climate
evolution~\cite{Dayan2008,kalashnikova} and monitoring air
quality. Mapping aerosol density is significant to aviation safety,
which needs real time assessment of conditions and visibility around
flight paths.

In remote sensing~\cite{Mishchenko2007}, imaging through air is associated with
{\em atmospheric correction}, based on {\em aerosol retrieval}. In
this discipline, the atmosphere is often assumed to be plane-parallel,
using one-dimensional vertical RT. Consequently state-of-the-art
aerosol retrieval is done in distinct large lateral
blocks~\cite{Martonchikc} with limited height
resolution~\cite{kalashnikova}. We, however, seek 3D
recovery. Atmospheric correction is related to
dehazing~\cite{Namer2009,Zhu2013}. In this paper, however, the medium
itself, at all relevant altitudes is the object of interest.

We rely on sky imaging from multiple directions and locations. Such
projection is similar to tomography in other scientific
domains~\cite{Bluestone2001}. However, the situation here is distinct. Most
tomography setups have a controlled and/or multidirectional radiation
source~\cite{Boas2001,messer}. In contrast, our source is the
uncontrolled, unidirectional Sun. Moreover, typical tomography relies
on a linear model~\cite{gregson}: the pixel value is a linear
combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect
gases~\cite{Kazahaya2008,Price2001,Cosofret2009,wright}, which absorb
UV or IR radiation. However, aerosol attenuation of visible light is
typically dominated by {\em scattering}, rather than absorption. Since
the radiation source is single and fixed in space and time, we cannot
rely on direct illumination for tomographic recovery of attenuation
fields~\cite{Aviles2011}. We may only use sunlight scattered into the
LOS. The model is {\em nonlinear, yet tractable}. We model passive
optical tomographic imaging of 3D atmospheric scatterer distributions
in cloudless conditions. Then, we solve this tomography problem, to
recover the distribution. Recovery is formulated as an optimization
that minimizes a cost function. We derive the gradient of this cost
function, to enable efficient optimization.
